Survivable Set Connectivity

### 2015-05-13 draft.tex
fixed a typo in 1.2

At this time, it seems that Survivable Set Connectivity is motivated primarily by theoreitcal interest, as a ``natural" generalization of Set Connectivity. It is unknown if any common real-life graph problems are naturally formulated as a Survivable Set Connectivity problem.

>>>>

At this time, it seems that Survivable Set Connectivity is motivated primarily by theoretical interest, as a ``natural" generalization of Set Connectivity. It is unknown if any common real-life graph problems are naturally formulated as a Survivable Set Connectivity problem.
